The four postulates of quantum mechanics are three

### 2020-11-05 Articles/2019-QuantumComposition/Submissions/PhysLetters/tensor.tex
Version submitted to PhysLetters

	%\fbox{{\scriptsize Preprint. \today}}
	\title{The four postulates of quantum mechanics are three}
	\author{Gabriele Carcassi$^1$, Lorenzo Maccone$^{2,*}$ and Christine A. Aidala$^1$
	}\affiliation{\vbox{1.~Physics Department, University of Michigan, 450 Church Street,
			Ann Arbor, MI 48109-1040,
			United States}\\
		\vbox{2.~Dip.~Fisica and INFN Sez.\ Pavia, University
			of Pavia, via Bassi 6, I-27100 Pavia, Italy}}
	\begin{abstract}
		The tensor product postulate of quantum mechanics states that the
		Hilbert space of a composite system is the tensor product of the
		components' Hilbert spaces. All current formalizations of quantum
		mechanics that do not contain this postulate contain some equivalent
		postulate or assumption (sometimes hidden). Here we give a natural
		definition of composite system as a set containing the component
		systems and show how one can logically derive the tensor product
		rule from the state postulate and from the measurement postulate. In
		other words, our paper reduces by one the number of postulates
		necessary to quantum mechanics.
	\end{abstract}
	\pacs{}
	% Measurement theory (quantum mechanics), 03.65.Ta Mechanics quantum,
	% 03.65.-w noise quantum, 42.50.Lc quantum information, 03.67.Ac
	% Quantum information, 03.67.-a Quantum fluctuations, 42.50.Lc quantum
	% mechanics, 03.65.Ta quantum optics, 42.50.Gy
	\maketitle

@@

	%%BoundingBox: 45 418 630 588
	%(%old BoundingBox: 45 382 649 547)
	\begin{figure}[ht]
		%\epsfxsize=1.\hsize\leavevmode\epsffile{fig.eps}
		\includegraphics[width=\linewidth, trim={0.2in 5.8in 2.5in 0.1in}, clip=true]{fig.eps}
		\caption{Schematic depiction of the logical implications used
			in this paper. FTPG stands for ``Fundamental Theorem of Projective Geometry''.  \label{f:fig}}\end{figure}

@@

	\togli{This axiomatization implicitly contains a definition of
		``quantum system'' which is crucial for what follows, so we need to
		clarify the assumptions that it contains. We will use the following
		definition for a quantum system\togli{$\stackon[1pt]={\mbox{\tiny
					def}}$}$\stackrel{\mbox{\tiny def}}=${\em ``a quantum degree
			of freedom with $d$ (possibly discrete, or continuous, infinite)
			mutually exclusive (commuting) values for each of its properties.
			Its mathematical description is through a Hilbert space of
			dimension $d$ which contains all the states that describe the
			values of its possible properties. In accordance with the
			postulate (a), these values correspond to a basis of the space,
			given by the eigenvectors of the observable corresponding to that
			property''}. \commentg{We may have to revise to be more clear.
			Where is this used?} } As stated above, we will limit ourselves to
	kinematically-independent systems, where all state vectors $|\psi\>$
	in the system's Hilbert space $\cal H$ describe a valid state, {\em
		unconditioned on anything else}. In particular, we note that
	restrictions due to superselection rules arise either from practical
	(not fundamental) limitations on the actions of the experimenter
	\cite{susskind,zanardi,zanardilloyd} or from the use of ill-defined
	quantum systems. For example, in situations where indistinguishability
	plays a role (e.g.~in QFT), one cannot consider an electron as a
	quantum system: in this case the quantum system is the field. The
	electron is an excitation of the field, {\em not} a (sub)system. We
	call this condition ``preparation independence''.  [We emphasize that
	the kinematic independence is inequivalent to dynamical independence
	(or isolation).  Indeed if two systems interact, their interaction may
	lead to dynamical restrictions in the state spaces. We will not
	consider dynamical evolution in this paper, which is contained in
	postulate (d).]

@@

	Since the square of the inner product is preserved, orthogonality and
	the hierarchy of subspaces are preserved through $M_b$, making $M_b$ a
	colinear transformation by definition. In this case, the fundamental
	theorem of projective geometry \cite{fun} applies, which tells us that
	a unique semi-linear map $m_b$ that acts on the vectors exists in accordance with $M_b$.
	Moreover, conservation of probability further constrains it to be
	either linear or antilinear. This tells us that the corresponding $m$
	is either linear or antilinear in the first argument. Namely, if equation
	\eqref{questa} holds, then
	\begin{align}
	\<a|\psi\>=\<m(a,b)|m(\psi,b)\>\labell{h2}\;
	\\\mbox{ or }
	\<a|\psi\>=\<m(\psi,b)|m(a,b)\> \labell{h2b}.
	\end{align}
	We can ignore the antilinear case \eqref{h2b}, which simply
	corresponds to the map $m$ mapping kets of one or both subsystems into
	bras before outputting the composite system (all these maps are
	trivially physically equivalent, since the dual-space description of a
	quantum system through bras is equivalent to the description using
	kets). We can now repeat the same analysis for the second argument of
	$m$ to conclude that it is a bilinear map, condition (H2).

@@

	We have obtained the conditions H1, H2 and H3 from the state postulate
	(a), the measurement postulate (b) and the definitions of composite
	and independent systems. In the methods section we prove that these
	three conditions imply that the (up to now unspecified) composition
	rule $m$ is the tensor product. More precisely, given a total,
	span-surjective, bilinear map $m:{\cal A}\times{\cal B}\to{\cal C}$
	that preserves the square of the inner product, we find that $\cal C $
	is equivalent to $\cal A \otimes \cal B $ and that $m=\otimes$.

	A few comments on the proof (given below): it is based on the universal
	property of the tensor product, which uniquely characterizes it. First
	we show that the bilinear map $m$ maps subsystems' bases into the
	composite system basis. We also know that there exists a tensor
	product map $ {T}=\otimes$ that can compose the vectors in $\cal A$
	and $\cal B$.  Then we use the universal property: since $m$ is a
	bilinear map, we are assured that there exists a unique $\hat m$ such
	that $\hat m \circ T=m$. Since we show that $\hat m$ is an
	isomorphism, then $\hat{m}$ bijectively maps vectors in $\cal C$ onto
	vectors in the tensor product space. Namely $m={T}=\otimes$.

@@

	\vskip 1\baselineskip
	{\par\noindent\bf Methods}

	Proof of the statement: {\em given a total, span-surjective, bilinear
		map $m:{\cal A}\times{\cal B}\to{\cal C}$ that preserves the square
		of the inner product, we find that $\cal C $ is equivalent to $\cal
		A \otimes \cal B $ and that $m=\otimes$.}

	Step 1: the bases of the component systems are mapped to a basis of
	the composite system. Because of totality property (H1) and because
	the square of the inner product is preserved, we can conclude that,
	given two orthonormal bases $\{|a_i\>\}\in{\cal A}$ and
	$\{|b_j\>\}\in{\cal B}$,
	$|\<m(a_i,b_j)|m(a_k,b_\ell)\>|^2=\delta_{ik}\delta_{j\ell}$, namely
	$\{|m(a_i,b_j)\>\}$ is an orthonormal set in $\cal C$.  Moreover, the
	surjectivity property (H3) guarantees that in $\cal C$ no vectors are
	orthogonal to this set. This implies that it is a basis for $\cal C$.

	\begin{references}
		\bibitem{zurek} W.H. Zurek, Quantum Darwinism, Nature Phys. {\bf 5},
		181 (2009).
		\bibitem{diracbook}P.A.M. Dirac, The principles of quantum mechanics,
		(Clarendon Press, Oxford, 1966).
		\bibitem{vonneumannbook}J. von Neumann, Mathematical Foundations of
		Quantum Mechanics (Princeton Univ.  Press, 1955).
		\bibitem{jauch}J.M. Jauch, Foundations of quantum mechanics
		(Addison-Welsey, 1968), pg.~176.
		\bibitem{weyl} H. Weyl, Gruppentheorie und Quantenmechanik (Hirzel,
		Leipzig, 1928); translated by H. P. Robertson, The Theory of Groups
		and Quantum Mechanics (Methuen, London, 1931); reprinted by Dover,
		p. 91.
		\bibitem{epr}A. Einstein, B. Podolsky, N. Rosen, Can
		quantum-mechanical description of physical reality be considered
		complete?, Phys. Rev. {\bf 47}, 777 (1935).
		\bibitem{ozawa}M. Ozawa, {Uncertainty relations for noise and
			disturbance in generalized quantum measurements}, Ann. Phys.  {\bf
			311}, 350 (2004).
		\bibitem{masanes}L. Masanes, T.D. Galley, M.P. M\" uller, The
		measurement postulates of quantum mechanics are operationally
		redundant, Nat. Commun. {\bf 10}, 1361 (2019).
		\bibitem{wootters}W.K. Wootters, Optimal Information Transfer and
		Real-Vector-Space Quantum Theory. In: Chiribella G., Spekkens R.
		(eds) Quantum Theory: Informational Foundations and Foils,
		Fundamental Theories of Physics, vol 181. Springer, Dordrecht
		(2016).
		\bibitem{nielsenchuang}M. A. Nielsen and I. L. Chuang, Quantum Computation
		and Quantum Information (Cambridge University Press, Cambridge,
		2000).
		\bibitem{ballentinebook}L.E. Ballentine, Quantum Mechanics, a modern
		development (World Scientific, 2014).
		\bibitem{ballentinepaper}L.E. Ballentine, Probability theory in
		quantum mechanics, Am. J. Phys. {\bf 54}, 883 (1986).
		\bibitem{peres}A.~Peres, Classical interventions in quantum systems.
		II. Relativistic invariance, Phys. Rev. A {\bf 61}, 022117 (2000).
		\bibitem{matolcsi} T. Matolcsi, Tensor product of Hilbert lattices and
		free orthodistributive product of orthomodular lattices, Acta Sci.
		Math. (Szeged), {\bf 37}, 263 (1975).
		\bibitem{marmo} F.M. Ciaglia, A. Ibort, G. Marmo, On the Notion of
		Composite System, In: Nielsen F., Barbaresco F. (eds) Geometric
		Science of Information, Lecture Notes in Computer Science, vol
		11712. Springer (2019).
		\bibitem{aerts} D. Aerts, I. Daubechies, Physical justification for
		using the tensor product to describe two quantum systems as one
		joint system, Helv. Phys. Acta {\bf 51}, 661 (1979).
		\bibitem{giddins}S.B.~Giddings, Hilbert space structure in quantum
		gravity: an algebraic perspective. J. High Energ. Phys. 2015, 1
		(2015).% https://doi.org/10.1007/JHEP12(2015)099
		\bibitem{roos}H. Roos, Independece of Local Algebras in Quantum Field
		Theory, Comm.  Math. Phys. {\bf 16}, 238 (1970).
		\bibitem{mipre}Z. Ji, A. Natarajan, T. Vidick, J. Wright, H. Yuen, MIP*=RE, arXiv:2001.04383 (2020). %https://quantumfrontiers.com/2020/03/01/the-shape-of-mip-re/
		\bibitem{susskind}Y. Aharonov, L. Susskind, Charge superselection
		rule, Phys. Rev. {\bf 155}, 1428 (1967).
		\bibitem{zanardi}P. Zanardi, Virtual Quantum Subsystems, Phys. Rev.
		Lett {\bf 87}, 077901 (2001).
		\bibitem{zanardilloyd} P. Zanardi, D.A. Lidar, S. Lloyd, Quantum
		Tensor Product Structures are Observable Induced, Phys. Rev. Lett.
		{\bf 92},060402 (2004).
		\bibitem{cox}R.T. Cox, The Algebra of Probable Inference (J. Hopkins
		press, 1961).
		\bibitem{fun} E. Artin: Geometric algebra, Interscience Publishers Inc (1957)
		\bibitem{tellerbook}P. Teller, An Interpretive Introduction to Quantum
		Field Theory (Princeton Univ. Press, 1997).  
		\bibitem{teller}M. Redhead, P. Teller, Particles, Particle Labels, and
		Quanta: The Toll of Unacknowledged Metaphysics, Found. Phys. {\bf
			21}, 43 (1991).
		\bibitem{hartle}J.B. Hartle, Quantum Mechanics of Individual Systems,
		Am. J.  Phys. {\bf 36}, 704 (1967).
	\end{references}

	\vskip 1\baselineskip
	{\bf Acknowledgements:} L.M. acknowledges useful discussions with
	M.~Ozawa, P.~Zanardi, S.~Lloyd, D.~Zeh, G.~Auletta, A.~Aldeni and
	funding from the Attract project through the Eu Horizon 2020 research
	and innovation programme under grant agreement No 777222. G.C. and
	C.A.A. would like to thank M. J. Greenfield for reviewing the mathematical details and acknowledge funding from the MCubed program of the University
	of Michigan.

	* Corresponding Author: maccone@unipv.it.

>>>>

%\fbox{{\scriptsize Preprint. \today}}
\title{The four postulates of quantum mechanics are three}
\author{Gabriele Carcassi$^1$, Lorenzo Maccone$^{2}$ and Christine A. Aidala$^1$
}\affiliation{\vbox{1.~Physics Department, University of Michigan, 450 Church Street,
	Ann Arbor, MI 48109-1040,
	United States}\\
  \vbox{2.~Dip.~Fisica and INFN Sez.\ Pavia, University
    of Pavia, via Bassi 6, I-27100 Pavia, Italy}}
\begin{abstract}
  The tensor product postulate of quantum mechanics states that the
  Hilbert space of a composite system is the tensor product of the
  components' Hilbert spaces. All current formalizations of quantum
  mechanics that do not contain this postulate contain some equivalent
  postulate or assumption (sometimes hidden). Here we give a natural
  definition of composite system as a set containing the component
  systems and show how one can logically derive the tensor product
  rule from the state postulate and from the measurement postulate. In
  other words, our paper reduces by one the number of postulates
  necessary to quantum mechanics.
\end{abstract}
\pacs{}
% Measurement theory (quantum mechanics), 03.65.Ta Mechanics quantum,
% 03.65.-w noise quantum, 42.50.Lc quantum information, 03.67.Ac
% Quantum information, 03.67.-a Quantum fluctuations, 42.50.Lc quantum
% mechanics, 03.65.Ta quantum optics, 42.50.Gy
\maketitle

@@

%%BoundingBox: 45 418 630 588
%(%old BoundingBox: 45 382 649 547)
\begin{figure}[ht]
\epsfxsize=1.\hsize\leavevmode\epsffile{fig.eps}
%\includegraphics[width=\linewidth, trim={0.2in 5.8in 2.5in 0.1in}, clip=true]{fig.eps}
\caption{Schematic depiction of the logical implications used
in this paper. FTPG stands for ``Fundamental Theorem of Projective Geometry''.  \label{f:fig}}\end{figure}

@@

\togli{This axiomatization implicitly contains a definition of
  ``quantum system'' which is crucial for what follows, so we need to
  clarify the assumptions that it contains. We will use the following
  definition for a quantum
  system\togli{$\stackon[1pt]={\mbox{\tiny
        def}}$}$\stackrel{\mbox{\tiny def}}=${\em ``a quantum degree
    of freedom with $d$ (possibly discrete, or continuous, infinite)
    mutually exclusive (commuting) values for each of its properties.
    Its mathematical description is through a Hilbert space of
    dimension $d$ which contains all the states that describe the
    values of its possible properties. In accordance with the
    postulate (a), these values correspond to a basis of the space,
    given by the eigenvectors of the observable corresponding to that
    property''}. \commentg{We may have to revise to be more clear.
    Where is this used?} } As discussed, we limit ourselves to
kinemati\-cal\-ly-inde\-pen\-dent systems, where all state vectors
$|\psi\>$ in the system's Hilbert space $\cal H$ describe a valid
state, {\em unconditioned on anything else}. In particular, we note
that restrictions due to superselection rules arise either from
practical (not fundamental) limitations on the actions of the
experimenter \cite{susskind,zanardi,zanardilloyd} or from the use of
ill-defined quantum systems. For example, in situations where
indistinguishability plays a role (e.g.~in QFT), one cannot consider
an electron as a quantum system: in this case the quantum system is
the field. The electron is an excitation of the field, {\em not} a
(sub)system. We call this condition ``preparation independence''.  [We
emphasize that the kinematic independence is inequivalent to dynamical
independence (or isolation).  Indeed if two systems interact, their
interaction may lead to dynamical restrictions in the state spaces.
Here we will not consider dynamical evolution, which is contained in
postulate (d).]

@@

Since the square of the inner product is preserved, orthogonality and
the hierarchy of subspaces are preserved through $M_b$, making $M_b$ a
colinear transformation by definition. In this case, the fundamental
theorem of projective geometry \cite{fun} applies, which tells us that
a unique semi-linear map $m_b$ that acts on the vectors exists in accordance with $M_b$.
Moreover, conservation of probability further constrains it to be
either linear or antilinear. This tells us that the corresponding $m$
is either linear or antilinear in the first argument. Namely, if equation
\eqref{questa} holds, then
\begin{align}
\<a|\psi\>=\<m(a,b)|m(\psi,b)\>\labell{h2}\;
 \\\mbox{ or }
\<a|\psi\>=\<m(\psi,b)|m(a,b)\> \labell{h2b}.
\end{align}
We can ignore the antilinear case \eqref{h2b}, which simply
corresponds to the map $m$ mapping kets of one or both subsystems into
bras before outputting the composite system. All these maps are
trivially physically equivalent, since the dual-space description of a
quantum system through bras is equivalent to the description using
kets, or in other words, the wavefunction and its complex-conjugate
contain identical information (for example, in his first papers
Schr\"odinger used both signs in his equation: effectively writing
{\em two} equivalent equations with complex-conjugate solutions
\cite{sch}). We can now repeat the same analysis for the second
argument of $m$ to conclude that it is a bilinear map, condition (H2).

@@

We have obtained the conditions H1, H2 and H3 from the state postulate
(a), the measurement postulate (b) and the definitions of composite
and independent systems. We now prove that these three conditions
imply that the (up to now unspecified) composition rule $m$ is the
tensor product. More precisely, given a total, span-surjective,
bilinear map $m:{\cal A}\times{\cal B}\to{\cal C}$ that preserves the
square of the inner product, we find that $\cal C $ is equivalent to
$\cal A \otimes \cal B $ and that $m=\otimes$.

Proof. Step 1: the bases of the component systems are mapped to a basis of
the composite system. Because of totality property (H1) and because
the square of the inner product is preserved, we can conclude that,
given two orthonormal bases $\{|a_i\>\}\in{\cal A}$ and
$\{|b_j\>\}\in{\cal B}$,
$|\<m(a_i,b_j)|m(a_k,b_\ell)\>|^2=\delta_{ik}\delta_{j\ell}$, namely
$\{|m(a_i,b_j)\>\}$ is an orthonormal set in $\cal C$.  Moreover, the
surjectivity property (H3) guarantees that in $\cal C$ no vectors are
orthogonal to this set. This implies that it is a basis for $\cal C$.

\vskip 1\baselineskip A few comments on the proof: it is based on the
universal property of the tensor product, which uniquely characterizes
it. First we show that the bilinear map $m$ maps subsystems' bases
into the composite system basis. We also know that there exists a
tensor product map $ {T}=\otimes$ that can compose the vectors in
$\cal A$ and $\cal B$.  Then we use the universal property: since $m$
is a bilinear map, we are assured that there exists a unique $\hat m$
such that $\hat m \circ T=m$. Since we show that $\hat m$ is an
isomorphism, then $\hat{m}$ bijectively maps vectors in $\cal C$ onto
vectors in the tensor product space. Namely $m={T}=\otimes$.

@@

{\it Acknowledgements:} L.M. acknowledges useful discussions with
M.~Ozawa, P.~Zanardi, S.~Lloyd, D.~Zeh, G.~Auletta, A.~Aldeni and
funding from the Attract project through the Eu Horizon 2020 research
and innovation programme under grant agreement No 777222. G.C. and C.A.A. would like to thank M. J. Greenfield for reviewing the mathematical details and acknowledge funding from the MCubed program of the University
	of Michigan.

\begin{references}
\bibitem{zurek} W.H. Zurek, Quantum Darwinism, Nature Phys. {\bf 5},
  181 (2009).
\bibitem{diracbook}P.A.M. Dirac, The principles of quantum mechanics,
  (Clarendon Press, Oxford, 1966).
\bibitem{vonneumannbook}J. von Neumann, Mathematical Foundations of
  Quantum Mechanics (Princeton Univ.  Press, 1955).
\bibitem{jauch}J.M. Jauch, Foundations of quantum mechanics
  (Addison-Welsey, 1968), pg.~176.
\bibitem{weyl} H. Weyl, Gruppentheorie und Quantenmechanik (Hirzel,
  Leipzig, 1928); translated by H. P. Robertson, The Theory of Groups
  and Quantum Mechanics (Methuen, London, 1931); reprinted by Dover,
  p. 91.
\bibitem{epr}A. Einstein, B. Podolsky, N. Rosen, Can
  quantum-mechanical description of physical reality be considered
  complete?, Phys. Rev. {\bf 47}, 777 (1935).
\bibitem{ozawa}M. Ozawa, {Uncertainty relations for noise and
    disturbance in generalized quantum measurements}, Ann. Phys.  {\bf
    311}, 350 (2004).
\bibitem{masanes}L. Masanes, T.D. Galley, M.P. M\" uller, The
  measurement postulates of quantum mechanics are operationally
  redundant, Nat. Commun. {\bf 10}, 1361 (2019).
\bibitem{wootters}W.K. Wootters, Optimal Information Transfer and
  Real-Vector-Space Quantum Theory. In: Chiribella G., Spekkens R.
  (eds) Quantum Theory: Informational Foundations and Foils,
  Fundamental Theories of Physics, vol 181. Springer, Dordrecht
  (2016).
\bibitem{nielsenchuang}M. A. Nielsen and I. L. Chuang, Quantum Computation
  and Quantum Information (Cambridge University Press, Cambridge,
  2000).
\bibitem{ballentinebook}L.E. Ballentine, Quantum Mechanics, a modern
  development (World Scientific, 2014).
\bibitem{ballentinepaper}L.E. Ballentine, Probability theory in
  quantum mechanics, Am. J. Phys. {\bf 54}, 883 (1986).
\bibitem{peres}A.~Peres, Classical interventions in quantum systems.
  II. Relativistic invariance, Phys. Rev. A {\bf 61}, 022117 (2000).
\bibitem{matolcsi} T. Matolcsi, Tensor product of Hilbert lattices and
  free orthodistributive product of orthomodular lattices, Acta Sci.
  Math. (Szeged), {\bf 37}, 263 (1975).
\bibitem{marmo} F.M. Ciaglia, A. Ibort, G. Marmo, On the Notion of
  Composite System, In: Nielsen F., Barbaresco F. (eds) Geometric
  Science of Information, Lecture Notes in Computer Science, vol
  11712. Springer (2019).
\bibitem{aerts} D. Aerts, I. Daubechies, Physical justification for
  using the tensor product to describe two quantum systems as one
  joint system, Helv. Phys. Acta {\bf 51}, 661 (1979).
\bibitem{giddins}S.B.~Giddings, Hilbert space structure in quantum
  gravity: an algebraic perspective. J. High Energ. Phys. 2015, 1
  (2015).% https://doi.org/10.1007/JHEP12(2015)099
\bibitem{roos}H. Roos, Independece of Local Algebras in Quantum Field
  Theory, Comm.  Math. Phys. {\bf 16}, 238 (1970).
\bibitem{mipre}Z. Ji, A. Natarajan, T. Vidick, J. Wright, H. Yuen, MIP*=RE, arXiv:2001.04383 (2020). %https://quantumfrontiers.com/2020/03/01/the-shape-of-mip-re/
\bibitem{susskind}Y. Aharonov, L. Susskind, Charge superselection
  rule, Phys. Rev. {\bf 155}, 1428 (1967).
\bibitem{zanardi}P. Zanardi, Virtual Quantum Subsystems, Phys. Rev.
  Lett {\bf 87}, 077901 (2001).
\bibitem{zanardilloyd} P. Zanardi, D.A. Lidar, S. Lloyd, Quantum
  Tensor Product Structures are Observable Induced, Phys. Rev. Lett.
  {\bf 92},060402 (2004).
\bibitem{cox}R.T. Cox, The Algebra of Probable Inference (J. Hopkins
  press, 1961).
\bibitem{fun} E. Artin: Geometric algebra, Interscience Publishers Inc (1957)
\bibitem{sch}E. Schr\"odinger, Annalen der Physik {\bf 102}, 81 (1926); English translation in E. Schr\"odinger, {\em Collected papers on Wave Mechanics} (Blackie \& Son, London, 1928).
\bibitem{tellerbook}P. Teller, An Interpretive Introduction to Quantum
  Field Theory (Princeton Univ. Press, 1997).  
\bibitem{teller}M. Redhead, P. Teller, Particles, Particle Labels, and
  Quanta: The Toll of Unacknowledged Metaphysics, Found. Phys. {\bf
    21}, 43 (1991).
\bibitem{hartle}J.B. Hartle, Quantum Mechanics of Individual Systems,
  Am. J.  Phys. {\bf 36}, 704 (1967).
\end{references}
